AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
polished heavily until prior to validation section

In this paper we propose the AA methodology and an associated software system
for coordinating distributed team work, tackling the disadvantages
of GSD. Team members take on an egalitarian role, and stay
voluntarily \textit{logged} in the system for part of their time
(e.g.\ 2 hours per day), during which they log a periodical short text
sentence or microlog --- similar to a ``tweet'' from Twitter --- as the
status of their activity. Logging is carried out using an easy a series of
available UI's: unix shell
commands, native GUI or web page, conventional social network posts, or chat messages to a log bot
listening to IRC, GTalk, G+, and others.  These ``microblog sentences'' are publicly aggregated and validated by other
team members. Through AA, we have a methodology and an associated system to help
implement and validate the activities of a distributed software team. It implicitly
legitimizes financial support for the expansion of the activity of the developer
team. The AA methodology is specially useful for coordinating distributed and
decentralized team work, providing effective means to asynchronously update
different team members without the need for synchronous unproductive meetings.

@@

From the developer's perspective, the AA methodology is based on
creating pretty small high perspective reports of what they are doing
in a specific time frame, that can be something between 5 to 15
minutes, depending on what is most convenient for the developer and the team. An
AA Session would be a period of at least 2 hours doing these periodical
micrologs. The developer can set reminders to show up when its time to
make a new report. The objective of the flexible time frame and
reminders is to minimize developer overhead during his AA session. In
this way he can make the reports while staying concentrated in his
code. Each report can be sent directly to an on-line server, or stored
locally in a temporarily database for sending later. This make
possible the use of AA while offline.

Developers can also record a video screencast in the end of the
session summarizing what has been done, explaining with his words and
showing his most important results. This, combined with the textual
log of his session, makes the whole report more understandable for
himself or other people searching for information about his
production.

@@

All AA reports made by the developers are sent to a Web server and
become public in a Website, being possible then for a manager or
another developer to follow very closely the work of a developer,
nearly real-time, reading each of his small reports of what he is
doing right now.

Another possibility is to check older sessions to see when sometimes
was done and the comments of the developer about it, since each AA
post happens in a very small time frame of work, the information about
what was done become very easy to understand, instead of a long
report in the end of a session.

The site is where the developer can add to his session a link for his
screencast about that session, a video summary of what was done to
complement the reports, useful specially on cases where the small
reports were done in a hurry, because the developer did not want to
lose his focus on something important at that moment.

>>>>

In this paper we propose the AA methodology and an associated software system
for coordinating distributed team work, tackling the disadvantages
of GSD. Team members take on an egalitarian role, and stay
voluntarily \textit{logged} in the system for part of their time
(e.g.\ 2 hours per day), during which they log a periodical short text
sentence or \emph{microlog} --- similar to a `tweet' from Twitter --- as the
status of their activity. Logging is carried out using an easy a series of
available UI's: unix shell
commands, native GUI or web page, conventional social network posts, or chat messages to a log bot
listening to IRC, GTalk, G+, and others.  These ``microblog sentences'' are publicly aggregated and validated by other
team members. Through AA, we have a methodology and an associated system to help
implement and validate the activities of a distributed software team. It implicitly
legitimizes financial support for the expansion of the activity of the developer
team. The AA methodology is specially useful for coordinating distributed and
decentralized team work, providing effective means to asynchronously update
different team members without the need for synchronous unproductive meetings.

@@

From the developer's perspective, the AA methodology is based on
creating pretty small high perspective reports of what they are doing
in a specific time frame, that can be something between 5 to 15
minutes, depending on what is most convenient for the developer and the team. An
\emph{AA Session} would be a period of at least 2 hours doing these periodical
\emph{micrologs} also called \emph{AA posts}. The developer can set reminders or alerts to show up when its time to
\emph{microlog}. The objective of the flexible time frame and
alert scheme is to \emph{minimize developer overhead} during his AA session. In
this way, the developer can issue micrologs while staying maximally concentrated in his
code. Each microlog may be sent directly to an on-line server, or stored
locally in a temporarily database for sending/pushing later. This enables
offline micrologging and periodical alerting.

Developers optionally record a \emph{video screencast} at the end of the
session summarizing what has been done, explaining with his words and
showing his most important results. This is very similar to the video logging system
in the movie Avatar~\cite{Avatar}, although it is proved from our July 2011 git repositories and online
wiki that we have used this powerful concept in AA prior to the release of
Avatar. Moreover, screencasting differs from general videologging in that it
typically captures actual workflow on
the computer screen. Screencasting, combined with the textual log of the AA
Session, renders the final report more understandable for the individual developer himself
or to other people searching for information about his production.

@@

All AA reports made by the developers are ultimatelly sent to a Web server and
become publically aggregated on a Website, enabling a manager or another
developer to follow very closely the work of a given developer, nearly real-time,
reading each of his small reports or micrologs of what he is doing right now.

Another use case is to check older sessions to check when certain tasks
were carried out and the comments of the developer about the \emph{process}.
Since each AA microlog happens in a very short timeframe of work, the information
about what was was done -- specially \emph{how} it was done -- becomes very easy to
understand, instead of a long report in the end of a session.

IN the current version of the AA server infrastructure, the aggregating
website is where the developer can attach a link for his
screencast about each session. Screencasts are specially useful on cases where
the small reports were done in a hurry, because the developer did not want to
lose his focus on something important at that moment.
